A Comparison of Neural Network Models for Water Quality Forecasting

### 2024-04-26 manuscript/manuscript.Rmd
Made some edits to Theta Forecaster; need to re-run that now

---
title: "A Comparison of Machine Learning Models for Water Quality Forecasting"
authors:
  - name: Marcus Lapeyrolerie
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: mlapeyro@berkeley.edu
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu (corresponding author)
abstract: |
  1. 
  2. 
  3. 
  4.

@@

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_oxygen.png}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_oxygen.png}
  \end{subfigure}

  \caption{Comparison of Historical and Naive Oxygen}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_temperature.png}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_temperature.png}
  \end{subfigure}

  \caption{Comparison of Historical and Naive temperature}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_chla.png}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_chla.png}
  \end{subfigure}

  \caption{Comparison of Historical and Naive chla}
\end{figure}

\begin{figure}[!htbp]
  \centering

  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_historical_oxygen.png}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_historical_temperature.png}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_historical_chla.png}
  \end{subfigure}

  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_naive_oxygen.png}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_naive_temperature.png}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_naive_chla.png}
  \end{subfigure}

@@

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/global_loc_historical_oxygen.png}
  \end{subfigure}

  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/date_type_global_historical_oxygen.png}
  \end{subfigure}

  \caption{Global performance on oxygen}
\end{figure}

>>>>

---
title: "A Comparison of Neural Network Models for Water Quality Forecasting"
authors:
  - name: Marcus Lapeyrolerie
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: mlapeyro@berkeley.edu
  - name: Carl Boettiger
    department: Department of Environmental Science, Policy, and Management
    affiliation: University of California, Berkeley
    location: Berkeley, California
    email: cboettig@berkeley.edu (corresponding author)
abstract: |
  1. 
  2. 
  3. 
  4.

@@

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_oxygen.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_oxygen.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive Oxygen}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_temperature.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_temperature.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive temperature}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_historical_chla.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/type_local_naive_chla.png}
  \end{subfigure}
  \caption{Comparison of Historical and Naive chla}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_historical_oxygen.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_naive_oxygen.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \rule{0pt}{0pt}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_historical_temperature.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_naive_temperature.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_historical_chla.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/intra_naive_chla.png}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \rule{0pt}{0pt}
  \end{subfigure}

@@

\begin{figure}[!htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/sitetype_legend.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/global_loc_historical_oxygen.png}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../plots/date_type_global_historical_oxygen.png}
  \end{subfigure}
  \caption{Global performance on oxygen}
\end{figure}
